Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\section{Introduction and related work}
A huge amount and variety of relational data are available in a wide range of fields. On the one hand, it provides an opportunity to build systems which automatically extract useful information. On the other hand, it raises challenges for machine learning and data scientists to design high performance predictive systems. A common data structure for representing relational data is graph whose nodes describe for entities and links depict their relations. We can easily see graph-based systems in different domains like biology, chemistry or networking. These systems require the data form used for their input as graphs. However, despite the availability of huge data, most graphs are only partially observed graphs. That means a number of actual links in each graph are absent or missing. Tackling this issue is a necessary condition to obtain high performance graph-based predictive systems. As a consequence, many link prediction methods have been proposed with the aim of recovering the missing links. A graph could be associated with external information sources, so called "side information". Therefore, a link prediction method attempts to exploit the graph topology and side information to build a the model for predicting the presence or absence of link any between couple of nodes. An expected method is required to make use of both such kind of data sources. In this paper, we only focus on the topological information. Thus we the term link prediction methods to refer to topology-based link prediction methods. Concerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.

@@

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose to a node labeling function $\ell$ such that nodes with similar degrees are assigned the same label. It is due to the assumption that nodes with similar degrees tend to share common properties. Following is the definition of the the function:
\begin{center}
$\ell(u) = \left\{
	\begin{array}{ll}
		d(u),\  & \mbox{if } d(u) \leq 5 \\
		6+i,\ & \mbox{if }  5 + \frac{d(G) - 5}{\lambda-5}*i \leq d(u) < 5 + \frac{d(G) - 5}{\lambda-5}*(i+1)
	\end{array}
\right.$,
\end{center}
where $\lambda > 5$ is the number of labels used to label for nodes in the graphs. The values of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
Most methods for link prediction attempt to computes similarities between nodes and consider to rank links. We desire to take links as examples to learn and predict. Therefore, we propose a method which model the context of two nodes to represent for link connecting them.

@@

\section{Results and Discussion}
Table \ref{result_table} shows the performance of link prediction methods in ROC-AUC on six datasets in which we mark as bold for the best ROC-AUC on each dataset. From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods. The performance of supervised methods are considerably higher than unsuperivsed ones in most cases, except in the Conflict dataset where Sup-Top outperforms Fact+Scores, but with a very small difference. Concerning supervised methods, JNSL outperforms Fact-Scores in all cases. The difference between their performance is small in PowerGrid and Protein datasets with 0.5$\%$ and 0.8$\%$, respectively.

>>>>

\section{Introduction and related work}
We are witnessing a constant increase of the rate at which data is being produced and made available in machine readable formats. Interestingly it is not only the quantity of data that is increasing, but also its complexity, i.e. not only are we measuring a number of attributes or features for each data point, but we are also capturing their mutual relationships, that is, we are considering data that is non independent and identically distributed (non i.i.d.). This yields collections that are best represented as graphs or relational data bases and requires a more complex form of analysis.

A huge amount and variety of relational data are available in a wide range of fields. On the one hand, it provides an opportunity to build systems which automatically extract useful information. On the other hand, it raises challenges for machine learning and data scientists to design high performance predictive systems. A common data structure for representing relational data is graph whose nodes describe for entities and links depict their relations. We can easily see graph-based systems in different domains like biology, chemistry or networking. These systems require the data form used for their input as graphs. However, despite the availability of huge data, most graphs are only partially observed graphs. That means a number of actual links in each graph are absent or missing. Tackling this issue is a necessary condition to obtain high performance graph-based predictive systems. As a consequence, many link prediction methods have been proposed with the aim of recovering the missing links. A graph could be associated with external information sources, so called "side information". Therefore, a link prediction method attempts to exploit the graph topology and side information to build a the model for predicting the presence or absence of link any between couple of nodes. An expected method is required to make use of both such kind of data sources. In this paper, we only focus on the topological information. Thus we the term link prediction methods to refer to topology-based link prediction methods. Concerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.

@@

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose to a node labeling function $\ell$ such that nodes with similar degrees are assigned the same label. It is due to the assumption that nodes with similar degrees tend to share common properties. Following is the definition of the the function:
\begin{center}
$\ell(u) = \left\{
	\begin{array}{ll}
		d(u),\  & \mbox{if } d(u) \leq 5 \\
		6+i,\ & \mbox{if }  5 + \left[ \frac{d(G) - 5}{\lambda-5} \right] *i \leq d(u) < 5 + \left[ \frac{d(G) - 5}{\lambda-5}\right] *(i+1)
	\end{array}
\right.$,
\end{center}
where $\lambda > 5$ is the number of labels used to label for nodes in the graphs. The value of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
Most methods for link prediction attempt to computes similarities between nodes and consider to rank links. We desire to take links as examples to learn and predict. Therefore, we propose a method which model the context of two nodes to represent for link connecting them.

@@

\section{Results and Discussion}
Table \ref{result_table} shows the performance of link prediction methods in ROC-AUC on six datasets in which we mark as bold for the best ROC-AUC on each dataset. From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods. The performance of supervised methods are considerably higher than unsuperivsed ones in most cases, except in the Conflict dataset where Sup-Top outperforms Fact+Scores, but with a very small difference. Concerning supervised methods, JNSL outperforms Fact-Scores in all cases. The difference between their performance is small in PowerGrid and Protein datasets with 0.5$\%$ and 0.8$\%$, respectively. And the big gap is in the Condmat dataset with 7.4$\%$.
